Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-15 paper/ms.tex
intro to simulated examples

>>>>

To demonstrate the application of \celerite, we will start by inferring
posterior constraints on the parameters of a GP model applied to several
simulated datasets with known properties.
In the following section, we will expand on these examples by applying
\celerite\ to real datasets.
In the first example, we demonstrate that \celerite\ can be used to measure
the power spectrum of a process when the data are generated from a \celerite\
model.
In the second example, we demonstrate that \celerite\ can be used as an
effective model even if the true process cannot be represented in the space of
allowed models.
This is a interesting example because, when analyzing real data, we rarely
have any fundamental reason to believe that the data were generated by a GP
model with a specific kernel.
Even in these cases, GPs can be useful effective models and \celerite\
provides computational advantages over other GP methods.
